Growth and inequality in public good provision --- an extended replication

### 2022-11-06 analysis/quarto/paper.tex
typo

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, frame hidden, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, breakable]}{\end{tcolorbox}}\fi

@@

Does this result hold true if one zooms in and inspects the two samples
separately? Yes. Even though the general population sample is a little
more consistent than the student sample, both are contributing more in
the abstract game than in the VCA.
Figure~\ref{fig-kernel-generalizability} shows distributions of
contributions across both choices for both samples. The left panels
illustrate the behavior of the general population sample. The right
panels illustrate the behavior of the general population sample. The top
panels show the behavior in the VCA. The bottom panels show the behavior
in first period of the game. A visual inspection shows that (a) both
samples behaved similarly in the first period of the game but (b)
different (p = 0.03) in the VCA. Furthermore, (c) the behavior in the
first period of the experiment predicts the general population sample's
behavior in the VCA worse than student sample's behavior (p = 0.07).
Finally, (4) contributions in the abstract public good game are higher
than contributions to the real public good of climate change mitigation.

>>>>

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

Does this result hold true if one zooms in and inspects the two samples
separately? Yes. Even though the general population sample is a little
more consistent than the student sample, both are contributing more in
the abstract game than in the VCA.
Figure~\ref{fig-kernel-generalizability} shows distributions of
contributions across both choices for both samples. The left panels
illustrate the behavior of the general population sample. The right
panels illustrate the behavior of the general population sample. The top
panels show the behavior in the VCA. The bottom panels show the behavior
in first period of the game. A visual inspection shows that (a) both
samples behaved similarly in the first period of the game but (b)
different (p = 0.03) in the VCA. Furthermore, (c) the behavior in the
first period of the experiment predicts the general population sample's
behavior in the VCA worse than student sample's behavior (p = 0.07).
Finally, (d) contributions in the abstract public good game are higher
than contributions to the real public good of climate change mitigation.
